Article Title

### 2020-06-19 paper/article_2.tex
updates

\section{Introduction}
In the last years, the precision of the Planck [cita] experiment, whose task was to analyse the Cosmic Microwave Background (CMB) anisotropies, has allowed to fully test our standard cosmological model $\Lambda$CDM which assumes the existence of Dark Energy ($\Lambda$) and Cold Dark Matter (CDM). In particular, in addition to the minimal 6 parameters describing $\Lambda$CDM, the CMB anisotropies allow to indirectly constrain other parameters, such as the current expansion rate of the Universe, $H_0$, whose inference strongly depends on the assumed cosmological model. For example, relaxing the spatial flatness hypothesis of our Universe or the constant equation of state for the dark energy, would change the estimated value of $H_0$.
\\
In parallel, the are other independent methods to measure $H_0$, such as the distance ladder [cita], water masers [cita], the time delay between multiple images of gravitational lensed quasars [cita H0LiCOW] and, in the future, gravitational waves [cita].
\\
In this paper we will focus on the gravitational lensing method, which allows to measure $H_0$, as firstly suggested by Refsdal [cita], with a weaker dependence on the cosmological parameters if compared to the CMB analyses.
%------------------------------------------------

@@

>>>>

\section{Introduction}
In the last years, the precision of the Planck [cita] experiment, whose task was to analyse the Cosmic Microwave Background (CMB) anisotropies, has allowed to fully test our standard cosmological model $\Lambda$CDM which assumes the existence of Dark Energy ($\Lambda$) and Cold Dark Matter (CDM). In particular, in addition to the minimal 6 parameters describing $\Lambda$CDM, the CMB anisotropies allow to indirectly constrain other parameters, such as the current expansion rate of the Universe, $H_0$, whose inference strongly depends on the assumed cosmological model. For example, relaxing the spatial flatness hypothesis of our Universe or the constant equation of state for the dark energy, would change the estimated value of $H_0$.
\\
In parallel, the are other independent methods to measure $H_0$, such as the distance ladder [cita], water masers [cita], the time delay between multiple images of gravitational lensed quasars [cita H0LiCOW] and, in the future, gravitational waves [cita].
\\
In this paper we will focus on the gravitational lensing method, which allows to measure $H_0$, as firstly suggested by Refsdal \cite{refsdal}, which has a weaker dependence on the cosmological parameters if compared to the CMB analyses.
%------------------------------------------------

@@

\bibitem{refsdal}
S. Refsdal,
\textit{MNRAS, 128, 307} (1964)
